\item
	Exercise 3.11.[2, p.61] Mrs S is found stabbed in her family garden. Mr S
	behaves strangely after her death and is considered as a suspect. On
	investigation of police and social records it is found that Mr S had beaten
	up his wife on at least nine previous occasions. The prosecution advances
	this data as evidence in favour of the hypothesis that Mr S is guilty of the
	murder. `Ah no,' says Mr S's highly paid lawyer, `\textit{statistically}, only one
	in a thousand wife-beaters actually goes on to murder his wife. So the
	wife-beating is not strong evidence at all. In fact, given the wife-beating
	evidence alone, it's extremely \textit{unlikely} that he would be the murderer of
	his wife - only a $1/1000$ chance. You should therefore find him innocent.'
	Is the lawyer right to imply that the history of wife-beating does not
	point to Mr S's being the murderer? Or is the lawyer a slimy trickster?
	If the latter, what is wrong with his argument?
	[Having received an indignant letter from a lawyer about the preceding
	paragraph, I'd like to add an extra inference exercise at this point: \textit{Does
	my suggestion that Mr. S.'s lawyer may have been a slimy trickster imply
	that I believe all lawyers are slimy tricksters?} (Answer: No.)]

\subsection*{Resposta}

Definindo as hipóteses:

\begin{itemize}
	\item $M$: Senhor S matou senhora S.
	\item $A$: Senhora S foi assassinada.
	\item $B$: Senhor S já bateu em senhora S.
	\item O advogado falou que $P(M|B)=\frac{1}{1000}$.
\end{itemize}

Pelo teorema de Bayes.

\[P(M|A,B) = \frac{{P(A|M,B)P(M,B)}}{{P(A|B)}}\]

É fácil ver que $P(A|M,B)=1$.

\[P(M|A,B) = \frac{{P(M,B)}}{{P(A|B)}}\]


O conjunto $A$ pode ser particionado em:

\begin{itemize}
	\item $M$: Senhor S assassinou senhora S.
	\item $O$: qualquer outra pessoa assassinou senhora S.
\end{itemize}

Temos duas razões diferentes.

\[\frac{{P(M,B)}}{{P(A|B)}}?\frac{{P(M,B)}}{{P(O|B)}}\]

É bem mais evidente que a fração da esquerda é maior que da direita. Logo,
o argumento do advogado é uma falácia.

% Solução completa na questão 6a
% https://ocw.mit.edu/courses/mathematics/18-05-introduction-to-probability-and-statistics-spring-2014/assignments/MIT18_05S14_ps5_solutions.pdf
